Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-08 article.tex
Removed the deleted parts

As illustrated in \cref{fig:groundgrid,fig:distributions},
the sky is discretized into a grid of $N_{\rm voxels}$ \rl{rectangular cuboid} volume elements
(voxels), indexed by $k$, $m$ or $q$.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/distributions}}
  \caption{\small Simulated 3D aerosol distributions: [a] {\em Haze
      blobs} and [b] {\em Haze Front}.  Here, an aerosol density unit
    is $10^{6}~{\rm particles}/{\rm m}^3.$ The atmopsheric domain has
    area of $50\times 50{\rm km}^2$, extending from the ground up to
    altitude of 10km. The domain is divided into a rectilinear grid
    having $N_{\rm voxels}$ voxels.}
  \label{fig:distributions}
\end{figure}
In a \emph{single-scattering} model, any SR changes direction only
once on the way to a camera. This model is valid in atmospheres that
are not very dense (inside fog and clouds this model does not
apply). \fix{In this model}{Here}, RT has three steps (\cref{fig:groundgrid}):
({\tt i})~Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii})~Light scattering at voxel
$k$, towards a camera. ~({\tt iii})~Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$ \del{as} (analyzed in
\cref{sec:optical-depth}).  Step~{\tt ii} involves the scattering
coefficient at voxel $k$ \del{described in} (\cref{sec:scattering}).

@@

Compounding the attenuation of irradiance along both $[{\rm SR},k]$
and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
(\cref{eq:beer-lambert,eq:tautotal,eq:alphabasic}) the \fix{the radiant power contributed by is}{voxel contributes} radiant power
\begin{equation}
  p_c(k)= L^{\rm TOA}
  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
  \exp[-\tau_c(k)]
  \;\;,
  \label{eq:ick}
\end{equation}
where $L^{\rm TOA}$ is the radiance at the TOA. A column-stack vector
of all voxel contributions is
\begin{equation}
  {\bm p}_c= L^{\rm TOA}
  (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c)
  \odot \exp(-\vect{\tau}_c)
  \;\;.
  \label{eq:pc}
\end{equation}

@@

The MC simulations rely on the same grid as
\cref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per pixel (\cref{fig:mcgrid}a):
\begin{figure}
  \centering
  \yoavcomment{\includegraphics{images/mcgrid.pdf}}
  \caption{\small [a] Multiple-scattering forward model by MC.
    [b] Photograph of the same sky and view point as in
    \cref{fig:simulation-results1}(a), rendered using MC.
    \del{[c] Cross section along the $X$-Axis of the MC simulation,
    single-scattering simulation and a single-scattering image created
    from the reconstructed distribution
    (Sec.~\ref{sec:optimization-results})}.}
  \label{fig:mcgrid}
\end{figure}

@@

\noindent ({\tt ii}) Find the distance on ray ${\cal R}_{i}$ to which
the photon-packet propagates. To do this, \cref{eq:taurand}
yields $\tau^{\rm random}$. Then, \cref{eq:lrand} generalizes to
a non-uniform atmosphere: using \cref{eq:tau}, numerically seek
$l^{\rm random}$ s.t.
\begin{align}
  \int_0^{l^{\rm random}}(\sigma^{\rm aerosol} n +\beta^{\rm air}) dl
  = \tau^{\rm random}
  \label{eq:MCextinct}
\end{align}
Distance $l^{\rm random}$ along ${\cal R}_{i}$ yields \del{the} 3D position ${\bf
  X}_{i}$.  If ${\bf X}_{i}$ is outside the atmospheric grid, the
packet is terminated. If, in addition, ${\cal R}_{i}\parallel {\rm
  SR}$ , the packet is counted as contributing to the image pixel.

\noindent ({\tt iii}) The type of particle (air molecule or aerosol)
that the photon-packet interacts with at point ${\bf X}_{i}$ is determined
randomly \fix{according to their relative densities at the voxel containing
${\bf X}_{i}$.}{The relative probabilities of this random step are set by the respective extinction coefficients
($\beta^{\rm air}$ vs. $\beta^{\rm aerosol}$) at the voxel containing ${\bf X}_{i}$.}

\noindent ({\tt iv}) If \fix{it}{the particle} is an aerosol, the photon-packet intensity
is attenuated to $I_{i+1}=\varpi^{\rm aerosol}I_{i}$. If $I_{i+1}$ is
lower than a threshold, the packet is stochastically terminated,
following~\cite{Iwabuchi2006}.

\noindent ({\tt v}) The photon-packet is scattered to a new direction,
determined by inverse transform sampling, according to the phase
function of the particle (Eqs.~\ref{eq:aerosol_scatter}
or~\ref{eq:rayleighP}). This yields a new {\em ray}, denoted ${\cal
  R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
estimation~\cite{marshak20053d} \fix{is used for calculating}{derives} the amount of
light back-traced to the sun at each scattering. The next iteration of
propagation (denoted {\tt ii} above) proceeds.

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}(a). \fix{A
comparison of a sample horizontal cross section is shown in
Fig.~\ref{fig:mcgrid}c.}
{Figure~\ref{fig:cross_sections} plots the intensity profile
along a horizontal cross section of the viewed field,
comparing photographs simulated using the single-scattering and the  MC forward models.
Figure~\ref{fig:cross_sections}(a) compares photographs Fig.~\ref{fig:simulation-results1}(d)
and Fig.~\ref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
This plot demonstrates consistency in this scene, for most pixels.
Figure~\ref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
where the aerosol density was increased ten folds (see Fig.~\ref{sec:optimization-results}
and the corresponding MC photograph Fig.~\ref{fig:simulation_particles}(d)).
In this plot the single-scattering and MC cross sections diverge
due to the effect of the high order scattering.}
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small \rl{Cross-sections along the $X$-axis of photographs rendered
    by the single-scattering (dotted) and MC (solid line) forward models.
    (a) cross sections of the {\em Haze Blobs} scene (Fig.~\ref{fig:simulation-results1}(d)
    and Fig.~\ref{fig:simulation_particles}(a)). The difference between the models is much more pronounced (b) 
    when the scatterers are ten times denser, corresponding to Fig.~\ref{fig:simulation_particles}(d).}
  }
  \label{fig:cross_sections}
\end{figure}

@@

When the type of aerosol above an area is known~\cite{Martonchik2009},
estimation of the density distribution $\DistUnknown$ is needed. The
data are $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
  measured}_c\}_{c=1}^{N_{\rm views}}$. Recovery is phrased as
optimization of a cost function that fits the image-formation model to
the data. Let $\DistSet$ be the set of all distributions complying
with some constraints.  Particularly, $\DistUnknown$ is non-negative,
and its spatial support is bounded between the ground and the TOA. The
optimization problem is
\begin{equation}
  \label{eq:minobjectiveA}
  \DistEstimated =
  \argmin_{\DistUnknown \in \DistSet} \CostFunc{\DistUnknown}
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  \CostFunc{\DistUnknown}
  = \sum_{c=1}^{N_{\rm views}}
  \left\|
    \MaskSun[{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})]
  \right\|^2_2  + \eta \Psi({\bm n}).
\end{equation}
Here $\MaskSun$ masks the area around the sun: \del{as} in real-world images
it is indeed blocked. \rl{We mask the horizon, by using a camera whose
field of view is a little narrower than hemispherical. This reduces
the influence of LOSs that are more strongly affected by high-order
scattering (Fig.~\ref{fig:scatter_order}(b)). Consequently,
the fit of the imaging model focuses on the bulk image region, where
the single scattering model is more valid.}  In \cref{eq:objectiveA},
$\Psi({\bm n})$ is a regularization term that expresses some prior
knowledge on the distribution, while $\eta$ is the regularization weight.

Since aerosol distributions are usually fuzzy, useful regularization
is by a {\em smoothness term}, which penalizes for energy in the second order
spatial derivatives (3D Laplacian), $\| \nabla^2{\bm
  n}\|^2_2$. Regularization is not required when data is sufficient
and reliable. \del{As seen in Fig.~\ref{fig:groundgrid},}Voxels at high
altitude have good coverage by many cameras at multiple directions (\cref{fig:groundgrid}),
while low altitude voxels are mainly observed by local
cameras. Hence, regularization can be weakened with altitude. We
accomplish this weakening using a weight
$w(k)=\exp\left[-h(k)/H^\mathrm{smooth}\right]$.  Overall we use
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| {\bf W} \Laplacian{\bm n}\|^2_2
\end{equation}
where $\Laplacian$ is a matrix representation of the 3D Laplacian
operator, and matrix ${\bf W}$ is diagonal, whose elements are $w(k)$.

@@

\rl{\noindent{\bf Forward models and distributions}:
Figure~\ref{fig:results} shows estimation results, corresponding to the
original distributions of Fig.~\ref{fig:distributions}.}
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/results}}
  \caption{\small \fix{Reconstructions of the}{Recoveries of} scenes shown in
    \cref{fig:distributions}. Color represents aerosol density\fix{. The density units are}{, in
    units of} $10^{6}~{\rm particles}/{\rm m}^3.$ In \fix{[a,b],
    single-scattering simulated images}{(a) and (b)
    images simulated by single-scattering} are used as input \fix{to}{for} the
    recovery.  In (c) and (d), MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
\rl{Here, the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Cameras were placed
$\sim 7$km apart on a $6\times6$ grid.
In Figs.~\ref{fig:results}(a) and \ref{fig:results}(b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and \ref{fig:results}(d), the MC model (multiple scattering)
rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested.
Overall, the distributions, the density order of magnitude and values are consistent.
Errors in Figs.~\ref{fig:results}(a) and \ref{fig:results}(b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in}
\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[t]
  \centering
  \begin{tabular}{cccccgg}
    \toprule
    Haze   & Forward        & Aerosol                 & Isotropic       & Absorbing & $\delta_{\rm mass}$ & $\epsilon~~$ \\
    scene  & model          & density [$1/{\rm m}^3$] & phase function? & aerosol?  &                     &              \\
     \midrule                                                                                             
    Front  & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & -1.1\%               & 18\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & 14\%               & 65\%         \\
    \cmidrule(r){1-5}                                                                                     
     Blobs & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 0\%                 & 14\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & -6.7\%               & 65\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ & $\surd$         &           & 2\%                & 49\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 & $\surd$   & -5.7\%               & 80\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{7})$ &                 &           & -23\%                & 98\%         \\
    \bottomrule
  \end{tabular}
  \caption{\rl{Relative errors in various simulations. Here ${\mathcal{O}}$ denotes order of magnitude.}}
  \label{tbl:mass}
\end{table}
\rl{the algorithm of} \cref{sec:inverse-problem}. \\

@@

We describe a way to sense the 3D atmosphere. It can help remote
sensing depart from common \fix{1D}{one-dimensional} aerosol distribution models, in favor
of detailed 3D RT analysis.  The paper describes both a novel data
acquisition system concept for this recovery task (ground-based camera
network), and a dedicated algorithm for reconstructing aerosol
distributions. Using more prior knowledge on the nature of
distributions will improve the recovery.

The estimation algorithm
uses a single scattering model. This approximation is valid when the
optical depth is small. However, as \del{the} MC simulations show, it is
important to generalize \st{is algorithm so that it explicitly
incorporates high-order scattering in the scene, including the
ground. This will certainly be needed for dense distributions as
clouds.}

\st{To deploy such a system on a very large scale will require a long-term
engineering effort. Camera specifications}~\cite{Pust2011}\st{should be
set to optimally recover a wide range of aerosol distributions. This
requires a major theoretic and numerical research.}
\rl{the recovery algorithm so that high-order scattering
is included in it. Such generalization would be computationally complex:
in our tests, the MC forward model was slower by 2-3 orders of magnitude
than a single-scattering analytic model. Thus, inverting a 3D multiple-scattering
model requires research into numerical schemes for increasing the solution
efficiency of both forward and inverse problems.
The remote sensing community has devised several approaches to better approximate
multiple-scattering problems, mainly in one-dimensional models (e.g., successive
orders of scattering and the discrete ordinates method). We may tap into some of these approaches.
Deploying an experimental system will be needed: camera specifications}~\cite{Pust2011}
\rl{should be set to optimally recover a wide range of aerosol distributions.}
%\hl{The relation between the quantity and spatial distribution of
%  cameras and the quality of reconstruction should also be determined.}
%\fix{This requires}{These open questions require} a major theoretic
% and numerical research.

@@

\fix{We thank David~J. Diner for useful discussions. Yoav Schechner is a
Landau Fellow - supported by the Taub Foundation. This work was
conducted in the Ollendorff Minerva Center. Minerva is funded through
the BMBF. Part of this work was performed at the Jet Propulsion
Laboratory, California Institute of Technology, under contract with
NASA.}{We are grateful to David~J. Diner for fruitful discussions and his support at all
levels. We thank the reviewers for useful comments. Yoav Schechner is a Landau
Fellow - supported by the Taub Foundation. This work is supported by the
US-Israel Binational Science Foundation (BSF grant 2012202) and conducted in the
Ollendorff Minerva Center. Minerva is funded through the BMBF. This work was supported
by NASA's Earth Science Technology Office Advanced Information Systems Technology Program.}

>>>>

As illustrated in \cref{fig:groundgrid,fig:distributions},
the sky is discretized into a grid of $N_{\rm voxels}$ \rl{rectangular cuboid} volume elements
(voxels), indexed by $k$, $m$ or $q$.
\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\columnwidth]{images/distributions}}
  \caption{\small Simulated 3D aerosol distributions: [a] {\em Haze
      blobs} and [b] {\em Haze Front}.  Here, an aerosol density unit
    is $10^{6}~{\rm particles}/{\rm m}^3.$ The atmopsheric domain has
    area of $50\times 50{\rm km}^2$, extending from the ground up to
    altitude of 10km. The domain is divided into a rectilinear grid
    having $N_{\rm voxels}$ voxels.}
  \label{fig:distributions}
\end{figure}
In a \emph{single-scattering} model, any SR changes direction only
once on the way to a camera. This model is valid in atmospheres that
are not very dense (inside fog and clouds this model does not
apply). \rl{Here}, RT has three steps (\cref{fig:groundgrid}):
({\tt i})~Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii})~Light scattering at voxel
$k$, towards a camera. ~({\tt iii})~Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$ (analyzed in
\cref{sec:optical-depth}).  Step~{\tt ii} involves the scattering
coefficient at voxel $k$ (\cref{sec:scattering}).

@@

Compounding the attenuation of irradiance along both $[{\rm SR},k]$
and $[{\rm LOS}_c,k]$, and scattering by voxel $k$ towards the camera
(\cref{eq:beer-lambert,eq:tautotal,eq:alphabasic}) the \rl{voxel contributes} radiant power
\begin{equation}
  p_c(k)= L^{\rm TOA}
  [\tilde{\alpha}^{\rm air}_c(k) + \tilde{\alpha}^{\rm aerosol}_c(k)]
  \exp[-\tau_c(k)]
  \;\;,
  \label{eq:ick}
\end{equation}
where $L^{\rm TOA}$ is the radiance at the TOA. A column-stack vector
of all voxel contributions is
\begin{equation}
  {\bm p}_c= L^{\rm TOA}
  (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm aerosol}_c)
  \odot \exp(-\vect{\tau}_c)
  \;\;.
  \label{eq:pc}
\end{equation}

@@

The MC simulations rely on the same grid as
\cref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per pixel (\cref{fig:mcgrid}a):
\begin{figure}
  \centering
  \yoavcomment{\includegraphics{images/mcgrid.pdf}}
  \caption{\small [a] Multiple-scattering forward model by MC.
    [b] Photograph of the same sky and view point as in
    \cref{fig:simulation-results1}(a), rendered using MC.
    }
  \label{fig:mcgrid}
\end{figure}

@@

\noindent ({\tt ii}) Find the distance on ray ${\cal R}_{i}$ to which
the photon-packet propagates. To do this, \cref{eq:taurand}
yields $\tau^{\rm random}$. Then, \cref{eq:lrand} generalizes to
a non-uniform atmosphere: using \cref{eq:tau}, numerically seek
$l^{\rm random}$ s.t.
\begin{align}
  \int_0^{l^{\rm random}}(\sigma^{\rm aerosol} n +\beta^{\rm air}) dl
  = \tau^{\rm random}
  \label{eq:MCextinct}
\end{align}
Distance $l^{\rm random}$ along ${\cal R}_{i}$ yields 3D position ${\bf
  X}_{i}$.  If ${\bf X}_{i}$ is outside the atmospheric grid, the
packet is terminated. If, in addition, ${\cal R}_{i}\parallel {\rm
  SR}$ , the packet is counted as contributing to the image pixel.

\noindent ({\tt iii}) The type of particle (air molecule or aerosol)
that the photon-packet interacts with at point ${\bf X}_{i}$ is determined
randomly \rl{The relative probabilities of this random step are set by the respective extinction coefficients
($\beta^{\rm air}$ vs. $\beta^{\rm aerosol}$) at the voxel containing ${\bf X}_{i}$.}

\noindent ({\tt iv}) If \rl{the particle} is an aerosol, the photon-packet intensity
is attenuated to $I_{i+1}=\varpi^{\rm aerosol}I_{i}$. If $I_{i+1}$ is
lower than a threshold, the packet is stochastically terminated,
following~\cite{Iwabuchi2006}.

\noindent ({\tt v}) The photon-packet is scattered to a new direction,
determined by inverse transform sampling, according to the phase
function of the particle (Eqs.~\ref{eq:aerosol_scatter}
or~\ref{eq:rayleighP}). This yields a new {\em ray}, denoted ${\cal
  R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
estimation~\cite{marshak20053d} \rl{derives} the amount of
light back-traced to the sun at each scattering. The next iteration of
propagation (denoted {\tt ii} above) proceeds.

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}(a). 
\rl{Figure~\ref{fig:cross_sections} plots the intensity profile
along a horizontal cross section of the viewed field,
comparing photographs simulated using the single-scattering and the  MC forward models.
Figure~\ref{fig:cross_sections}(a) compares photographs Fig.~\ref{fig:simulation-results1}(d)
and Fig.~\ref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
This plot demonstrates consistency in this scene, for most pixels.
Figure~\ref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
where the aerosol density was increased ten folds (see Fig.~\ref{sec:optimization-results}
and the corresponding MC photograph Fig.~\ref{fig:simulation_particles}(d)).
In this plot the single-scattering and MC cross sections diverge
due to the effect of the high order scattering.}
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small \rl{Cross-sections along the $X$-axis of photographs rendered
    by the single-scattering (dotted) and MC (solid line) forward models.
    (a) cross sections of the {\em Haze Blobs} scene (Fig.~\ref{fig:simulation-results1}(d)
    and Fig.~\ref{fig:simulation_particles}(a)). The difference between the models is much more pronounced (b) 
    when the scatterers are ten times denser, corresponding to Fig.~\ref{fig:simulation_particles}(d).}
  }
  \label{fig:cross_sections}
\end{figure}

@@

When the type of aerosol above an area is known~\cite{Martonchik2009},
estimation of the density distribution $\DistUnknown$ is needed. The
data are $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
  measured}_c\}_{c=1}^{N_{\rm views}}$. Recovery is phrased as
optimization of a cost function that fits the image-formation model to
the data. Let $\DistSet$ be the set of all distributions complying
with some constraints.  Particularly, $\DistUnknown$ is non-negative,
and its spatial support is bounded between the ground and the TOA. The
optimization problem is
\begin{equation}
  \label{eq:minobjectiveA}
  \DistEstimated =
  \argmin_{\DistUnknown \in \DistSet} \CostFunc{\DistUnknown}
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  \CostFunc{\DistUnknown}
  = \sum_{c=1}^{N_{\rm views}}
  \left\|
    \MaskSun[{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})]
  \right\|^2_2  + \eta \Psi({\bm n}).
\end{equation}
Here $\MaskSun$ masks the area around the sun: in real-world images
it is indeed blocked. \rl{We mask the horizon, by using a camera whose
field of view is a little narrower than hemispherical. This reduces
the influence of LOSs that are more strongly affected by high-order
scattering (Fig.~\ref{fig:scatter_order}(b)). Consequently,
the fit of the imaging model focuses on the bulk image region, where
the single scattering model is more valid.}  In \cref{eq:objectiveA},
$\Psi({\bm n})$ is a regularization term that expresses some prior
knowledge on the distribution, while $\eta$ is the regularization weight.

Since aerosol distributions are usually fuzzy, useful regularization
is by a {\em smoothness term}, which penalizes for energy in the second order
spatial derivatives (3D Laplacian), $\| \nabla^2{\bm
  n}\|^2_2$. Regularization is not required when data is sufficient
and reliable. Voxels at high
altitude have good coverage by many cameras at multiple directions (\cref{fig:groundgrid}),
while low altitude voxels are mainly observed by local
cameras. Hence, regularization can be weakened with altitude. We
accomplish this weakening using a weight
$w(k)=\exp\left[-h(k)/H^\mathrm{smooth}\right]$.  Overall we use
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| {\bf W} \Laplacian{\bm n}\|^2_2
\end{equation}
where $\Laplacian$ is a matrix representation of the 3D Laplacian
operator, and matrix ${\bf W}$ is diagonal, whose elements are $w(k)$.

@@

\rl{\noindent{\bf Forward models and distributions}:
Figure~\ref{fig:results} shows estimation results, corresponding to the
original distributions of Fig.~\ref{fig:distributions}.}
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/results}}
  \caption{\small \rl{Recoveries of} scenes shown in
    \cref{fig:distributions}. Color represents aerosol density\rl{, in
    units of} $10^{6}~{\rm particles}/{\rm m}^3.$ In \rl{(a) and (b)
    images simulated by single-scattering} are used as input \rl{for} the
    recovery.  In (c) and (d), MC simulated images are used as input for the
    recovery.  }
  \label{fig:results}
\end{figure}
\rl{Here, the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Cameras were placed
$\sim 7$km apart on a $6\times6$ grid.
In Figs.~\ref{fig:results}(a) and \ref{fig:results}(b), the single-scattering model was
used both in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and \ref{fig:results}(d), the MC model (multiple scattering)
rendered the raw images, over which our recovery (Sec.~\ref{sec:inverse-problem}) was tested.
Overall, the distributions, the density order of magnitude and values are consistent.
Errors in Figs.~\ref{fig:results}(a) and \ref{fig:results}(b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in}
\newcolumntype{g}{>{\columncolor{Gray}}r}
\begin{table}[t]
  \centering
  \begin{tabular}{cccccgg}
    \toprule
    Haze   & Forward        & Aerosol                 & Isotropic       & Absorbing & $\delta_{\rm mass}$ & $\epsilon~~$ \\
    scene  & model          & density [$1/{\rm m}^3$] & phase function? & aerosol?  &                     &              \\
     \midrule                                                                                             
    Front  & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & -1.1\%               & 18\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & 14\%               & 65\%         \\
    \cmidrule(r){1-5}                                                                                     
     Blobs & Single scatter & ${\mathcal{O}}(10^{6})$ &                 &           & 0\%                 & 14\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 &           & -6.7\%               & 65\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ & $\surd$         &           & 2\%                & 49\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{6})$ &                 & $\surd$   & -5.7\%               & 80\%         \\
           & Monte Carlo    & ${\mathcal{O}}(10^{7})$ &                 &           & -23\%                & 98\%         \\
    \bottomrule
  \end{tabular}
  \caption{\rl{Relative errors in various simulations. Here ${\mathcal{O}}$ denotes order of magnitude.}}
  \label{tbl:mass}
\end{table}
\rl{the algorithm of} \cref{sec:inverse-problem}. \\

@@

We describe a way to sense the 3D atmosphere. It can help remote
sensing depart from common \rl{one-dimensional} aerosol distribution models, in favor
of detailed 3D RT analysis.  The paper describes both a novel data
acquisition system concept for this recovery task (ground-based camera
network), and a dedicated algorithm for reconstructing aerosol
distributions. Using more prior knowledge on the nature of
distributions will improve the recovery.

The estimation algorithm
uses a single scattering model. This approximation is valid when the
optical depth is small. However, as MC simulations show, it is
important to generalize 
\rl{the recovery algorithm so that high-order scattering
is included in it. Such generalization would be computationally complex:
in our tests, the MC forward model was slower by 2-3 orders of magnitude
than a single-scattering analytic model. Thus, inverting a 3D multiple-scattering
model requires research into numerical schemes for increasing the solution
efficiency of both forward and inverse problems.
The remote sensing community has devised several approaches to better approximate
multiple-scattering problems, mainly in one-dimensional models (e.g., successive
orders of scattering and the discrete ordinates method). We may tap into some of these approaches.
Deploying an experimental system will be needed: camera specifications}~\cite{Pust2011}
\rl{should be set to optimally recover a wide range of aerosol distributions.}
%\hl{The relation between the quantity and spatial distribution of
%  cameras and the quality of reconstruction should also be determined.}
%\fix{This requires}{These open questions require} a major theoretic
% and numerical research.

@@

\rl{We are grateful to David~J. Diner for fruitful discussions and his support at all
levels. We thank the reviewers for useful comments. Yoav Schechner is a Landau
Fellow - supported by the Taub Foundation. This work is supported by the
US-Israel Binational Science Foundation (BSF grant 2012202) and conducted in the
Ollendorff Minerva Center. Minerva is funded through the BMBF. This work was supported
by NASA's Earth Science Technology Office Advanced Information Systems Technology Program.}
